Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-05-31 manuscript.Rmd
cite popper

This sounds like a truism but is directly related to Popper's famous criterion of demarcation.
He stated that if it is impossible to prove a hypothesis false, therefore $P(E|¬H) = 1$ or conversely $P(¬E|¬H) = 0$, it can not be a scientific hypothesis (Popper 1962, 39).
We note these relations to underline that the Bayesian rational we apply here is able to reconstruct many commonly held views on riskiness and epistemic value.

>>>>

This sounds like a truism but is directly related to Popper's famous criterion of demarcation.
He stated that if it is impossible to prove a hypothesis false, therefore $P(E|¬H) = 1$ or conversely $P(¬E|¬H) = 0$, it can not be a scientific hypothesis [@popperLogicScientificDiscovery2002, p. 18].
We note these relations to underline that the Bayesian rational we apply here is able to reconstruct many commonly held views on riskiness and epistemic value.
